Incentivizing Exploration with Unbiased History

### 2018-11-02 intro-intro.tex

>>>>

\nicomment{a proposed abstract since i don't have the token on main.tex:}

In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.  A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.  A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.  The goal of the algorithm is to minimize the regret of the action sequence.

In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.  One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.

\nicomment{and now for the intro to the intro.}

In {\em incentivized exploration}, a recommendation algorithm presents a sequence of agents

In social learning, a sequence of individuals choose actions based on observations of past choices.  Incentivized exploration algorithms coordinate social learning, hiding inducing sufficient exploration

### 2018-11-02 intro.tex

@@

\xhdr{Our contributions.}
We build one such conceptual framework for a particular type of disclosure policies. Consider the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}. However, for the sake of the argument, what if the policy reveals the history for every other agent, rather than the history for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user is chosen in advance, without looking at the observations. In particular, the disclosure policy cannot subsample the observations that make a particular action look good.

>>>>

\xhdr{Our contributions.}
We start by revisiting the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}. However, for the sake of the argument, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution. In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.

With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time. Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$. So, agent $t$ has all information that agent $t'$ had at the time she chose her action. In particular, agent $t$ does not need to second-guess which message has caused aget $t'$ to make choose that action.

@@
